Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-06 agda.tex
working on #6
updating text to reflect that everything is proven

This development is available in the supplemental material. At the time of submission, the full set of rules is available and the proofs of Theorem \ref{thrm:actsafe}, Theorem \ref{lemma:movement-erasure} and a number of technical lemmas that we elided or mentioned informally in the text are complete. We also have nearly all of the cases of Reachability and Constructability complete, and we see no major barrier to the remaining cases -- we prioritized developing a clear exposition of our contributions after proving representative cases and finding that they were straightforward. The remaining cases will be completed in the repository linked in the non-anonymous supplementary material.\todo{talk about determinism either here or there}

The documentation 
includes a more detailed discussion of the technical representation
decisions that we made. The main idea is standard: we encode each judgement as a
dependent type. The rules defining the judgements become the constructors of this
type, and derivations are terms of these type. This is a rich
setting that allows proofs to take advantage of pattern matching on the
shape of derivations, closely matching standard on-paper proofs. No proof automation was used, because the proof structure itself is likely to be interesting to researchers who plan to build upon our work. 
% The formalization differs from the calculus defined here in a few small 
% ways. Most interestingly, instead of giving separate movement rules for each 
% form of Z-expression, we abstract
% over different corresponding forms that happen to have the same arity, e.g. 
% additions and applications. Formalizing this intuition
% reduces the number of cases we need to consider 
% somewhat, but more importantly allows us to write a slightly more
% general calculus -- it will be easier to extend Hazelnut with more 
% interesting language features with this generic infrastructure in place.
We adopt Barendregt's convention for
bound variables \cite{urban}. Hazelnut's semantics does not need substitution, so we do not need to adopt more sophisticated encodings (e.g. \cite{lh09unibind,Pouillard11}.)

>>>>

This development is available in the supplemental material. It contains the
full set of rules given in the paper, and proofs of all of the theorems
described. It also contains the rules needed for the extension to the
language described in Sec. \ref{sec:extending}, and extends the proofs to
the constructs.

The documentation includes a more detailed discussion of the technical
representation decisions that we made. The main idea is standard: we encode
each judgement as a dependent type. The rules defining the judgements
become the constructors of this type, and derivations are terms of these
type. This is a rich setting that allows proofs to take advantage of
pattern matching on the shape of derivations, closely matching standard
on-paper proofs. No proof automation was used, because the proof structure
itself is likely to be interesting to researchers who plan to build upon
our work.

We adopt Barendregt's convention for bound
variables \cite{urban}. Hazelnut's semantics does not need substitution, so
we do not need to adopt more sophisticated encodings
(e.g. \cite{lh09unibind,Pouillard11}.)
